\section{Related Work}
\label{sec:related}

\para{LLM-based forecasting.} Recent work has explored using LLMs to estimate probabilities for future events. \citet{logprob2025} use log probabilities to generate novel forecasts with calibrated probabilities, achieving Brier scores competitive with prediction markets. \citet{outcomedriven2025} fine-tune models using Polymarket outcomes via self-play and DPO, reaching GPT-4o parity with smaller models. \citet{forecastbench2024} introduce a dynamic benchmark showing that frontier LLMs approach but do not match human superforecasters, while \citet{aiaforecaster2025} achieve superforecaster-level performance with a multi-agent architecture and Platt scaling calibration. These works focus on producing accurate \emph{probabilities}; we build on their insights to produce accurate \emph{narratives}.

\para{Calibration and evaluation.} LLM forecasting systems face systematic calibration challenges. \citet{kalshibench2025} show that all frontier models are overconfident on prediction market questions, with reasoning enhancements worsening calibration. \citet{prophet2025} introduce Causal Intervened Likelihood to identify which questions are answerable from available evidence, finding that agentic RAG outperforms naive approaches. \citet{lu2025} evaluate 12 frontier models against expert forecasters and find that narrative-style prompting \emph{decreases} forecast accuracy---a key finding that motivates our separation of forecasting and narrative generation into distinct pipeline stages.

\para{Market-conditioned generation.} \citet{mentionmarkets2026} demonstrate that LLMs and prediction markets are complementary, proposing Market-Conditioned Prompting (\mcp) where market probabilities serve as Bayesian priors that LLMs update with textual evidence. Their MixMCP approach achieves the best Brier scores on Kalshi earnings mention markets. We adapt this framework from probability estimation to full article generation, treating resolved market outcomes as conditioning signals rather than priors to be updated.

\para{Temporal reasoning and future text.} \citet{timer1_2025} train a 3B-parameter model via progressive reinforcement learning that matches 671B models on temporal tasks, including future headline generation. Their AvgMaxSim metric measures semantic similarity between generated and real events. \citet{news2forecast2024} demonstrate the inverse pipeline---using news events to improve time series forecasting---while \citet{fakemarkets2025} show that framing LLM evaluation as a fictional prediction market elicits better-calibrated confidence signals.

\para{Human-AI forecasting collaboration.} \citet{aiaugmented2024} show that LLM assistants improve human forecasting accuracy by 24--28\%, with superforecaster-prompted assistants yielding 41\% improvement. \citet{promptforecasting2025} systematically compare prompting strategies for LLM forecasting, providing best practices that inform our prompt design.

\para{Positioning.} Unlike prior work that focuses on probability estimation, we evaluate the generation of complete news articles conditioned on market data. Our work is closest to \citet{mentionmarkets2026} in using market conditioning, but we target narrative generation rather than probability refinement, and to \citet{timer1_2025} in generating future-oriented text, but we ground our generation in prediction market data rather than temporal patterns alone.
